Critical Temperature of YBCO and BSCCO Superconductors

### 2014-11-22 Draft.tex
intro/method

\title{Critical Temperature of Superconductors YBCO and BSCCO}
% In a long title you can use \\ to force a line break at a certain location.

@@

\section{Procedure}
The YBCO and BSCCO superconductors were obtained from Colorado Superconductor Inc. Each superconductor  is contained in a brass casing with two pairs of leads. One pair is attached to the current source and the other pair was used to measure voltage across the superconductor. The casing also contains a thermocouple, which has a resistance that varies with temperature. We measure the voltage across the thermocouple to find the temperature of superconductor. We used different methods to measure the critical temperature of the two superconductors.

For the YBCO, we connected to an alternating current source of 1 mA. 
\section{Results and Analysis}

>>>>

\title{Critical Temperature of YBCO and BSCCO Superconductors}
% In a long title you can use \\ to force a line break at a certain location.

@@

\section{Procedure}
The YBCO and BSCCO superconductors were obtained from Colorado Superconductor Inc. Each superconductor  is contained in a brass casing with three pairs of leads. 
One pair was for attaching to the current source, another pair was used to measure voltage across the superconductor, and the last pair that of the thermocouple inside the casing. 
The thermocouple has a resistance that varies with temperature, so we can determine the  temperature of superconductor by measuring the voltage across the thermocouple.

We used different methods to measure the critical temperature of the two superconductors.
For the YBCO, we connected it to a source with an alternating current of $\pm$1 mA. The voltage across the YBCO sample, $V_{\textrm{YBCO}}$, and the voltage across the thermocouple, $V_{T}$ were measured with two nanovoltmeters. We placed the supeconductor inside a styrofoam cup filled with sand. The sand reduces the rate at which the superconductor heats up, which allows us to gather more data points. We cooled the YBCO sample by pouring liquid nitrogen into the styrofoam cup. We monitored the thermocouple voltage to check when the temperature of the  sample settled to a minimum.  
\section{Results and Analysis}
